---
title: "Tables and Figures"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message=FALSE, warning=FALSE)
```



```{r, echo=FALSE, eval=F}
source("analysis.R")
```

<!--
Make Base Tables with analysis.R

Currently Stargazer does not support making a caption above descriptive variables 
(unlike regression output with dep.var.caption)

Edit Tables with Line (Tables 1-3)
%insert mod
 &&& \multicolumn{3}{c}{Proportions (N)} \\ \cline{4-6} \\[-4.8ex]  \\
\hline \\[-1.8ex] 
%end mod

Edit Tables with Line (Table 4)
%insert mod
 && \multicolumn{3}{c}{Proportions (N)} \\ \cline{3-5} \\[-4.8ex]  \\
\hline \\[-1.8ex] 
%end mod

bash
$for file in *.tex; do cp $file ${file%%.*}edit.tex; done
-->

```{r, child='tables/table1edit.tex', eval=T}
```


```{r, child='tables/table2edit.tex', eval=T}
```


```{r, child='tables/table3edit.tex', eval=T}
```


```{r, child='tables/table4edit.tex', eval=T}
```



```{r, child='tables/table1.tex', eval=F}
```


```{r, child='tables/table2.tex', eval=F}
```


```{r, child='tables/table3.tex', eval=F}
```

```{r, child='tables/table4.tex', eval=F}
```




\begin{figure}[h]
		\centering
		\includegraphics[width=1.0\textwidth]{./images/plt1.png}
		\caption[Figure 1]{Matched Reports of Officer Involved Shootings - Dallas Police Department by Crowdsource}
\end{figure}


\begin{figure}[h]
		\centering
		\includegraphics[width=1.0\textwidth]{./images/plt2.png}
		\caption[Figure 1]{Matched Reports of Officer Involved Shootings - Denver Police Department by Crowdsource}
\end{figure}


\begin{figure}[h]
		\centering
		\includegraphics[width=1.0\textwidth]{./images/plt3.png}
		\caption[Figure 1]{Matched Reports of Officer Involved Shootings - All Police Departments by Crowdsource}
\end{figure}
